Gammapy: A Python package for gamma-ray astronomy

### 2023-03-21 src/ms-review.tex
Proposal for the text about time-based analysis
Signed-off-by: Bruno Khélifi <khelifi@in2p3.fr>

With the v1.0 release, the \gammapy project enters a new development
phase. Future work will not only include maintenance of the v1.0 release,
but also parallel development of new features, improved API and data
model support. While v1.0 provides all the features required for
standard and advanced astronomical \gammaray data analysis,
we already identified specific improvements to be considered in the
roadmap for a future v2.0 release. This includes the support for
scalable analyses via distributed computing. This will allow
users to scale an analysis from a few observations to multiple
hundreds of observations as expected by deep surveys of the CTA
observatory. In addition the high-level interface
of \gammapy is planned to be developed into a fully configurable
API design. This will allow users to define arbitrary complex analysis
scenarios as YAML files and even extend their workflows by user defined
analysis steps via a registry system. Another important topic will
be to improve the support of handling metadata for data structures
and provenance information to track the history of the data reduction
process from the DL3 to the highest DL5/DL6 data levels. \gammapy will
also extend its functionality for time based analyses, including
tests for variability in lightcurves and phase curves as well as
improving the interoperabiltiy with other timing packages such
as \textit{Stingray}~\citep{Stingray2019} and \textit{Astropy's}
time series classes.

>>>>

With the v1.0 release, the \gammapy project enters a new development
phase. Future work will not only include maintenance of the v1.0 release,
but also parallel development of new features, improved API and data
model support. While v1.0 provides all the features required for
standard and advanced astronomical \gammaray data analysis,
we already identified specific improvements to be considered in the
roadmap for a future v2.0 release. This includes the support for
scalable analyses via distributed computing. This will allow
users to scale an analysis from a few observations to multiple
hundreds of observations as expected by deep surveys of the CTA
observatory. In addition the high-level interface
of \gammapy is planned to be developed into a fully configurable
API design. This will allow users to define arbitrary complex analysis
scenarios as YAML files and even extend their workflows by user defined
analysis steps via a registry system. Another important topic will
be to improve the support of handling metadata for data structures
and provenance information to track the history of the data reduction
process from the DL3 to the highest DL5/DL6 data levels. \gammapy will
also extend its functionalities for time based analyses,
e.g. tests for variability in light curves, phase curves peak search, 
as well as improving the interoperability with other timing packages such
as \textit{Stingray}~\citep{Stingray2019}, \textit{Astropy's}
time series classes or \textit{pint-pulsar}~\citep{Luo2021}
 for high-precision pulsar timing.
